\chapter{Validation}\label{ch:validation}
In this section we will talk about the testing part of the project. In particular our purpose was to 
show that the system satisfy the requirements listed in ~\ref{ch:analysis}. \\
In order to do that we wrote some test that consider different case for esch state of the car:
\begin{itemize}
    \item [a.] on each side, and on the bridge itself, there aren't any cars, except the one we are testing;
    \item [b.] on the same side of our car there is another one in position -1 or 1 depending on the side, 
    while on the other one there is nobody;
    \item [c.] on the opposite side there is a car.
\end{itemize}

\subsection{Tests}
Our tests check the correct flow of events. In other words we wanted to find out if the car in a 
particular situation (defined by the environment) reacts to it sending and receiving the expected
events. The car should also act as we wanted so that there is no accident, deadlock, starvation and so on.

\section{Functional requirements}

We were able to check if the system can:
\begin{itemize}
    \item \textbf{Coordinate the traffic}.
    \item \textbf{Avoid} any kind of \textbf{accident}.
    \item Avoid situation where more than $n$ cars, where $n$ is the capacity, cross the the bridge at 
    the same time.
    \item Make cars cars interchange messages due to decide correctly who can cross, after reached an
    (\textbf{agreement}), the bridge.
    \item Detect \textbf{broken} cars and remove them calling a tow truck.
    \item generate new cars.
\end{itemize}


\section{Non functional requirements}

For the non functional requirements we tested that:
\begin{itemize}
    \item \textbf{Safety}: the system guarantees that the bridge can be crossed only by cars that 
        are moving in the same direction, but also that if a car broke, the others are able to detect that
        and so they stop before crashing into it. 
    \item \textbf{Strength}: the system is usable even if a car breaks down and needs to be removed.
    \item \textbf{Scalability}: incrementing number of cars, clients and web services, the system don't affect
    too much the whole system.
    \item \textbf{Starvation}: when a car requires to cross the bridge, the request will be satisfied 
    eventually. 
    \item \textbf{Fairness}: the crossing order is a \textbf{FIFO ordering}.
\end{itemize}

